---
title: "recruitment-visualization-process"
format: html
---

## Data wrangling and cleaning

Several modifications are required for the dynamic coral data prior to functional analysis. The following coding block details handling missing data and establishing a shared color gradient for each taxa.

```{r}
#| message: false
#| warning: false
#| code-fold: true
library(tidyverse)
library(ggthemes)
# clean_coral <- read_csv(here::here("vedika-r-files", "data", "coral_tidy_dyn_2013-2024 - coral_tidy_dyn_2013-2024.csv"), na = c("UK", "MK", "?", "MD", "US", "NS", "MissingObs", "Na", "NA"))

clean_coral <- read_csv(here::here("vedika-r-files", "data", "volume_corals.csv"))


# Coral color way - consistent across all visualizations

coral_colors <- c(
 Acr = "blue", 
 Poc = "red", 
 Por = "darkgreen", 
 Mil = "darkorange"
)

clean_coral <- clean_coral |> 
  # Removing plots from backreef surveys 
  filter(str_detect(transect, "T")) |> 
# Change volume variables to numeric
  mutate(
    height = as.numeric(height),
    width  = as.numeric(width),
    length = as.numeric(length),
      # Create volume (cm^2), z (m), and y (m) columns  
     y_m = y / 100, 
     z_m = z /100, 
    # Acropora were input as "A" in 2024, converting to "Acr" 
    taxa = case_when(taxa == "A" ~ "Acr", 
                     TRUE ~ taxa)) 



```

## Plotting Recruitment Overtime at Transects

The function `transect-recruitment` is sourced locally from the `recruitment-visual-function.R` file stored in this repository. This function is intended to create the total standardized recruitment per year at each transect for a specified site. Each figure generated is stored in its respective subfolder (`transect-site-recruitment`).

```{r}
source(here::here("vedika-r-files", "recruitment-visual-function.R"))
source(here::here("vedika-r-files", "recruitment-compiled-function.R"))
```

```{r, fig.height = 5, fig.width=9}
# Generate plots for each transect (ex. at site LTER1 for BR)
#transect_recruitment(coral_data = clean_coral, site_name = "LTER2", habitat = "BR")

# Transect-level recruitment across all sites and habitats
p <- plot_recruitment(
  coral_data = clean_coral
  #facet_level = "habitat"
)

ggsave(
     "recruitment_plot.png",
     plot = p,
     width = 10,
     height = 5,
     bg = "transparent" 
   )

```

## Plotting Recruitment Overtime at Sites

The function `site-recruitment` is sourced locally from the `recruitment-visual-function.R` file stored in this repository. This function is intended to create the total standardized recruitment per year at each site for a specified habitat across all taxa. Each figure generated will be stored in its respective subfolder (`transect-site-recruitment`).

```{r}
#| warnings: false
#| message: false
# Generate plots for each site at a specific habitat
site_recruitment(coral_data = clean_coral, habitat_name = "BR")
```

## Plotting Recruitment Overtime at Each Habitat

The function `habitat-recruitment` is sourced locally from the `recruitment-visual-function.R` file stored in this repository. This function is intended to create the total standardized recruitment per year at each habitat across all taxa.

```{r}
# Generate plots for each habitat 
habitat_recruitment(clean_coral)
```

```{r}
coral <- read_csv(here("vedika-r-files", "data", "volume_corals.csv"))

source(here("survival", "R", "survival_fig_function.R"))
source(here::here("combined_demography", "demography_function.R"))
```

```{r}
# Initalize coral color palette
coral_colors <- c(
    Acr = "blue", 
    Poc = "red", 
    Por = "darkgreen", 
    Mil = "darkorange"
  )

coral_death <- coral %>% 
  group_by(coral_number) %>%
  arrange(year) %>% 
  mutate(survival = case_when(
    dyn_death == 1 ~ 0,
    is.na(length) ~ NA,
    TRUE ~ 1
  ), volume = case_when(
    is.na(size_t0) ~ size_t_minus1,
    TRUE~ size_t0
  )
  ) %>% 
  ungroup()

```

```{r}
survival_plot(data = coral_death, site = "LTER2", habitat = "BR")
plot_recruitment()
```

```{r}
## Let's practice with combine demographic function
demography_plot(data = clean_coral,
  profile_filter = "survival",
  site_filter = "LTER1",
  habitat_filter = "BR",
  by_transect = T)


######
demography_plot_test(
  data = clean_coral,
  profile_filter = "growth",
  site_filter = "LTER1",
  habitat_filter = "BR",
  by_transect = TRUE
)

#### 
demography_plot(
  data = clean_coral,
  profile_filter = "survival",
  site_filter = "LTER1",
  habitat_filter = "BR",
  by_transect = F
)

```
