---
title: "recruitment-visualization-process"
format: html
---

## Data wrangling and cleaning

Several modifications are required for the dynamic coral data prior to functional analysis. The following coding block details handling missing data and establishing a shared color gradient for each taxa.

```{r}
#| warning: false
#| message: false
#| collapse: true
library(tidyverse)
clean_coral <- read_csv(here::here("vedika-r-files", "data", "coral_tidy_2024_with_dynamics.csv"), na = c("UK", "MK", "?", "MD", "US", "NS", "MissingObs", "Na", "NA"))

# Coral color way - consistent across all visualizations
coral_colors <- c(
  Acr = "blue", 
  Poc = "red", 
  Por = "darkgreen", 
  Mil = "darkorange"
)

clean_coral <- clean_coral |> 
  # Removing plots from backreef surveys 
  filter(str_detect(transect, "T")) |> 
  # Change volume variables to numeric
  mutate(
    height = as.numeric(height),
    width  = as.numeric(width),
    length = as.numeric(length),
    # Create volume (cm^2), z (m), and y (m) columns  
    y_m = y / 100, 
    z_m = z /100, 
    # Acropora were input as "A" in 2024, converting to "Acr" 
    taxa = case_when(taxa == "A" ~ "Acr", 
                     TRUE ~ taxa)) 


```

## Plotting Recruitment Overtime at Transects

The function `transect-recruitment` is sourced locally from the `recruitment-visual-function.R` file stored in this repository. This function is intended to create the total standardized recruitment per year at each transect for a specified site. Each figure generated is stored in its respective subfolder (`transect-site-recruitment`).

```{r}
library(sourcetools)
source(here::here("vedika-r-files", "recruitment-visual-function.R"))
```

```{r, fig.asp = .8}
# Generate plots for each transect (ex. at site LTER1 for BR)
transect_recruitment(coral_data = clean_coral, site_name = "LTER2", habitat = "OR")
```

## Plotting Recruitment Overtime at Sites 

The function `site-recruitment` is sourced locally from the `recruitment-visual-function.R` file stored in this repository. This function is intended to create the total standardized recruitment per year at each site for a specified habitat across all taxa. Each figure generated is stored in its respective subfolder (`transect-site-recruitment`).

```{r, fig.asp= .8}
# Generate plots for each site at a specific habtat
site_recruitment(coral_data = clean_coral, habitat_name = "BR")
```

## Plotting Recruitment Overtime at Each Habitat

The function `habitat-recruitment` is sourced locally from the `recruitment-visual-function.R` file stored in this repository. This function is intended to create the total standardized recruitment per year at each habitat across all taxa.

```{r}
habitat_recruitment(clean_coral)
```
